---
title: "Homework 1"
author: Wenzhao Wu
output: github_document
---

This is my solution to HW1.

```{r}
library(tidyverse)
```


## Problem 1

Create a data frame with the specified elements.

```{r}
prob1_df = 
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a","b","c","d","e","f","g","h","i","j"),
    factor_vec = factor(c("low","low","low","mod","mod","mod","mod","high","high","high"))
)
```

Take the mean of each variable in my data frame.

```{r}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

I can take the mean of numbers and logical but not character or factor. 

```{r}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```

```{r}
as.numeric(pull(prob1_df, samp_gt_0))*pull(prob1_df, samp)
as.factor(pull(prob1_df,samp_gt_0))*pull(prob1_df, samp)
as.numeric(as.factor(pull(prob1_df,samp_gt_0)))*pull(prob1_df, samp)
```

## Problem 2

```{r}
data("penguins", package = "palmerpenguins")
```

The "penguins" includes data about `r ls(penguins)`. 
  These characteristics are collected from species: `r levels(pull(penguins, species))`. They are from different islands, including `r levels(pull(penguins, island))`.  
  The sex includes: `r levels(pull(penguins, sex))`.  
  According to the data of all species, the bill length is in a range of (`r range(pull(penguins, bill_length_mm), na.rm = TRUE)`) mm, the bill depth is between (`r range(pull(penguins, bill_depth_mm), na.rm = TRUE)`) mm, the flipper length has a range of (`r range(pull(penguins, flipper_length_mm), na.rm = TRUE)`) mm, and the body mass has a range of (`r range(pull(penguins, body_mass_g), na.rm = TRUE)`) g.  
  This dataset contains `r nrow(penguins)` rows and `r ncol(penguins)` columns.  
  The mean of flipper length is `r mean(pull(penguins, flipper_length_mm), na.rm=TRUE)` mm. 
